Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-07-16 drafts/outline.tex
Updates from Overleaf

Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure 1). Effective particle capture efficiency (\(\eta\prime=p_r\frac{b_c}{d_c}\)) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention (\(p_r\)) as a multiplicand in its calculation. This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that leave $p_r$ as an implicit factor.

\begin{figure}[htbp]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \marginnote{Figure borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}[-5cm]}
\end{figure}

@@

TODO: Flume floorplan figure

@@

We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities. We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains. We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA). Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure 2).

\begin{figure}[htbp]
\includegraphics[width=15cm,trim = {0 3cm 0 0},clip]{wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
\end{figure}

>>>>

Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure \ref{fig:capeff}). Effective particle capture efficiency (\(\eta\prime=p_r\frac{b_c}{d_c}\)) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention (\(p_r\)) as a multiplicand in its calculation. This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that leave $p_r$ as an implicit factor.

\begin{figure}[htbp]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:capeff}
\end{figure}

@@

\begin{figure}[htbp]
TODO
\centering
\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:floorplan}
\end{figure}

@@

We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities. We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains. We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA). Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure \ref{fig:sedsize}).

\begin{figure}[htbp]
\includegraphics[width=15cm,trim = {0 3cm 0 0},clip]{wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
\label{fig:sedsize}
\end{figure}
